---
title: "Project-1"
output: html_document
date: "2024-03-29"
---

# 0. Functions:

## 0.1. Show most significant correlation matrix

```{r}
disp_sig_corrMat <- function(data_par, type_of_correlation, max_N){
}
```

## 0.2 Hot encoding categorical data into numericals

```{r}
hot_encode <- function(data_par, column_par){
  for (column in data_par){
    
  }
}
```

# Project 1

## 1. Data pre-processing

### 1.1. Data loading

```{r}
library(tidyverse)
library(magrittr) # Pipe implementation for R
library(data.table) # Implements %like%
data <- read_csv("Files/speeddating.csv", col_names = TRUE, num_threads = 4) # Read data into R
head(data,5)
```

### 1.2. Data exploration

```{r}
#Check data
View(data)                  # View table
# Getting data dimensions
dim(data)                   # View dimensions of table
lobstr::obj_size(data)      # View memory size of table
# Data summary
table(sapply(data, class))  # View class info of table
typeof(data)                # View type of table
```

From thees informations we have come to several conclusion:

1.  Data set is sufficient for our needs (project specifications)
2.  Observations are inter-independent
3.  These data are long data
4.  Number of categorical attributes is too big for our following processing \<-- It will be needed to encode it
5.  Several of attributes are intervals

### 1.3 Null values

```{r}
sum(is.na(data))
```

We have found zero null values in dataset, in this case there is no need for futher modifications of dataset, for this reason.

### 1.4. Data reduction
